\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}

### 2020-10-21 arxiv_full_version/main.tex
appendix
arxiv full version

\def\shownotes{0}
\usepackage{natbib}
\setcitestyle{authoryear,open={(},close={)}}
\renewcommand{\cite}{\citep}
\usepackage[export]{adjustbox}
\usepackage[margin=1in]{geometry}
%\usepackage{fullpage}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{macro_math}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage{multirow}
\usepackage[us,12hr]{datetime}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{caption,subcaption}
%\usepackage{breqn}

@@

\title{\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}}
\vspace{0.15in}
\author[1]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu.}}
\author[2]{Fan Yang\samethanks}
\author[3]{Sen Wu}
\author[2]{Weijie S. Su}
\author[3]{Christopher R\'e}
\vspace{0.15in}
\affil[1]{Khoury College of Computer Sciences, Northeastern University}
\affil[2]{Department of Statistics, Wharton School, University of Pennsylvania}
\affil[3]{Department of Computer Science, Stanford University}

@@

\subsection*{Acknowledgements:}
Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
HZ and SW's contributions were in part supported by Wharton Dean's Fund for Postdoctoral Research.

>>>>

\def\shownotes{1}
\usepackage{natbib}
\setcitestyle{authoryear,open={(},close={)}}
\renewcommand{\cite}{\citep}
\usepackage[export]{adjustbox}
\usepackage[margin=1in]{geometry}
%\usepackage{fullpage}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{macro_math}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage{multirow}
\usepackage[us,12hr]{datetime}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{caption,subcaption}
%\usepackage{breqn}

@@

\title{\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}}
\vspace{0.15in}
\author[1]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu or fyang75@wharton.upenn.edu.}}
\author[2]{Fan Yang\samethanks}
\author[3]{Sen Wu}
\author[2]{Weijie J. Su}
\author[3]{Christopher R\'e}
\vspace{0.15in}
\affil[1]{Khoury College of Computer Sciences, Northeastern University}
\affil[2]{Department of Statistics, Wharton School, University of Pennsylvania}
\affil[3]{Department of Computer Science, Stanford University}

@@

\subsection*{Acknowledgements:}
Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
HZ and WS's contributions were in part supported by Wharton Dean's Fund for Postdoctoral Research.
We gratefully acknowledge the support of DARPA under Nos. FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No. U54EB020405 (Mobilize), NSF under Nos. CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No. N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, [STANFORD/STUDENT-SPECIFIC FELLOWSHIPS], and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys. The U.S. Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S. Government.

### 2020-10-21 arxiv_full_version/same_cov.tex
arxiv full version

\begin{theorem}\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
	For any task $i = 1, 2, \dots, t$, with high probability over the randomness of the input, the prediction loss of $\hat{\beta}_i^{\MTL}$ satisfies that
	\begin{align*}
		\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}}
		\le n^{-\frac{c_{\varphi}}2} \cdot \frac{t \bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2}^2} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}.
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align*}
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
\end{theorem}

>>>>

\begin{theorem}\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
	For any task $i = 1, 2, \dots, t$, with high probability over the randomness of the input, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that
	\begin{align*}
		\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}}
		\le n^{-\frac{c_{\varphi}}2} \cdot \frac{t \bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2}^2} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}.
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align*}
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
\end{theorem}
